---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.12.0
  kernelspec:
    display_name: R
    language: R
    name: ir
---

<!-- #region nbgrader={"grade": false, "grade_id": "cell-f1e1d845873036f4", "locked": true, "schema_version": 3, "solution": false, "task": false} -->
# Worksheet 6: Difference between Causation and Association, and Model Diagnostics
<!-- #endregion -->

<!-- #region nbgrader={"grade": false, "grade_id": "cell-82d9926086d47a80", "locked": true, "schema_version": 3, "solution": false, "task": false} -->
#### Lecture and Tutorial Learning Goals:
After completing this week's lecture and tutorial work, you will be able to:

1. Describe heteroscedasticity and the problem it presents to generative modeling.
2. Write a computer script to assess whether heteroscedasticity in a given data set, and if so, use practical solutions to manage it.
3. Describe colinearity and the problem it presents to generative modeling.
4. Write a computer script to assess whether collinearity exists between input variables in a given data set, and if so, use practical solutions to manage it.
5. Discuss what model diagnostics the data scientist can do by themselves and when the data scientist needs to consult a domain expert.
6. Give an example of a real problem that aims to test a causal relationship between variables.
7. Give an example of a real problem the model can only establish an association between the response and the input variables.
8. Discuss how the desired goal of generative modelling is usually to make causal claims however we cannot often/easily do so (e.g., in particular in the context of observational studies).
9. Discuss the role of confounders in causal inference.
<!-- #endregion -->

```{r nbgrader={'grade': False, 'grade_id': 'cell-a2a153352bc44a68', 'locked': True, 'schema_version': 3, 'solution': False, 'task': False}}
# Run this cell before continuing.
library(tidyverse)
library(repr)
library(digest)
library(infer)
library(cowplot)
library(broom)
install.packages("faux")
library(faux)
source("tests_worksheet_06.R")
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-382d4cff30ea6f88"} -->
## 1. Warm Up Questions
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-bc69a71d9089848d"} -->
**Question 1.0**
<br>{points: 1}

True or false?

In an observational study, a correlation between a response variable and an input variable can be interpreted as causal effect.

*Assign your answer to an object called `answer1.0`. Your answer should be either "true" or "false", surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-64e4d3903f7a544f'}}
# answer1.0 <- ...

### BEGIN SOLUTION
answer1.0 <- "false"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-dc6e70215d392be2'}}
test_1.0()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-e09a0361f4541bf3"} -->
**Question 1.1**
<br>{points: 1}

True or false?

The results of the test of hypotheses given by `lm()` are only valid if we assume that the errors in the linear regression model are (exactly) Normally distributed.

*Assign your answer to an object called `answer1.1`. Your answer should be either "true" or "false", surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-44f5390242e66448'}}
# answer1.1 <- ...

### BEGIN SOLUTION
answer1.1 <- "false"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-8fed7ee78a3eb713'}}
test_1.1()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-0cd72706949e2df2"} -->
**Question 1.2**
<br>{points: 1}

True or false?

In a linear regression, multicollinearity refers to the correlation between each input variable with the response variable.

*Assign your answer to an object called `answer1.2`. Your answer should be either "true" or "false", surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-dcf5e346ae4d23b2'}}
# answer1.2 <- ...

### BEGIN SOLUTION
answer1.2 <- "false"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-9c7fa20462d3583a'}}
test_1.2()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-b081691974727e18"} -->
**Question 1.3**
<br>{points: 1}

True or false?

In the presence of multicollinearity in a multiple linear regression (MLR), it can be difficult to determine how collinear variables are separately associated with the response.

*Assign your answer to an object called `answer1.3`. Your answer should be either "true" or "false", surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-2e7e71146f6c4cf0'}}
# answer1.3 <- ...

### BEGIN SOLUTION
answer1.3 <- "true"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-3e42935abf1a7270'}}
test_1.3()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-bfd0d54d4d051503"} -->
**Question 1.4**
<br>{points: 1}

True or false?

Multicollinearity inflates the estimates of the standard errors of the least squares (LS) estimators of the regression coefficients.

*Assign your answer to an object called `answer1.4`. Your answer should be either "true" or "false", surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-77075476489b956d'}}
# answer1.4 <- ...

### BEGIN SOLUTION
answer1.4 <- "true"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-b1048804f31dc9ea'}}
test_1.4()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-9c2b725ee6ef8b19"} -->
**Question 1.5**
<br>{points: 1}

True or false?

The assumption that all the error terms have the same variance does not affect the estimates of the standard error of the LS estimators.

*Assign your answer to an object called `answer1.5`. Your answer should be either "true" or "false", surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-71b8eca6f72e054f'}}
# answer1.5 <- ...

### BEGIN SOLUTION
answer1.5 <- "false"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-212dc805b92990b7'}}
test_1.5()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-a7afce7a95d0bf98"} -->
# PART I
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-fa599c4dd2ab0c31"} -->
## 2. Model Diagnostics

When we analyze a dataset to respond to a question of interest, we make several assumptions. However, in practice, many of these assumptions may not be true posing many problems in our analysis. The most common problems that we may encounter are:

1. the relation between the response and the input variable(s) is not linear
2. error terms are correlated (not independent as we assumed)
3. error terms do not have a common variance (not identically distributed as we assumed)
4. error terms are not Normally distributed (not a strong assumption but convenient)
5. (some) input variables are correlated

"In practice, identifying and overcoming these problems is as much an
art as a science" (from ISL, Section 3.3.3). 

In this worksheet we will explore how these problems affect our estimation and analyses using simulated data. The advantage of simulating data is that we have full control over the data generating process so we know the "true" parameters and we can introduce problems in a control way. Real datasets are rich and interesting but usually contain many (unknown) problems and we don't know the true parameters to assess the performance of our estimation and analyses.
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-0352fabc6efebd45"} -->
**Question 2.0**
<br>{points: 1}

Let's start by generating a sample of size $n = 1000$ from a data generating process that fullfills all the assumptions of classical linear regression with a continuous response, one continuous input variable and one binary input variable. We call this first sample `sample_model_1`.

That is, for $i = 1, \dots, n$:

$$Y_i = \beta_0 + \beta_1 X_{i1} + \beta_2 X_{i2} + \varepsilon_i$$ 

where the error terms $\varepsilon_i \sim \mathcal{N}(0, \sigma^2 = 4)$ are independent and identically distributed. 

Assume that the true (population) regression terms $\beta_0$, $\beta_1$, and $\beta_2$ are $10$, $8$, and $5$ and generate a random sample of size $n = 1000$. 

We will assume that $X_{1}$ is a continuous random variable with values uniformly distributed between 2 and 5 and $X_{2}$ is a binary random variable with levels "A" and "B" (with equal probabilty).

> **Heads up**: the distributions used to generate the input variables do not affect the results of our analysis. 

Note that the columns of `sample_model_1` are:

- `x_1`: the values of the continuous input $X_{i1}$.
- `x_2`: the levels of the discrete input $X_{i2}$.
- `y`: the sampled response values $Y_i$.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-5005e2d15ce1ed92'}}
sample_size <- 1000

set.seed(123) # DO NOT CHANGE!

# sample_model_1 <- tibble(
#   x_1 = runif(n = ..., ..., ...),
#   x_2 = factor(rbinom(n = ..., size = 1, prob = 0.5), , labels=c("A", "B"))
# )
# sample_model_1$y <- ... + 8 * sample_model_1$x_1 + 5 * ifelse(sample_model_1$x_2 == "B", 1, 0) +
#   rnorm(n = ..., mean = ..., sd = ...)
# head(sample_model_1)

### BEGIN SOLUTION
set.seed(123)

sample_model_1 <- tibble(
  x_1 = runif(n = sample_size, 2, 5),
  x_2 = factor(rbinom(n = sample_size, size = 1, prob = 0.5), labels=c("A", "B"))
)

sample_model_1$y <- 10 + 8 * sample_model_1$x_1 + 5 * ifelse(sample_model_1$x_2 == "B", 1, 0) +
  rnorm(n = sample_size, mean = 0, sd = 2)
  
head(sample_model_1)

### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-4cb5c9662c07edb1'}}
test_2.0()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-37e2698a76960ba7"} -->
**Question 2.1**
<br>{points: 1}

Use the simulated `sample_model_1` to estimate the regression parameters $\beta_0$, $\beta_1$, and $\beta_2$ and elements to make inference using hypothesis tests. Use the functions `lm()` and assign the results to the object `model_1`.

Obtain the estimated coefficients, their standard errors, corresponding $p$-values, $95/%$ confidence intervals using `tidy()`. Store the results in `model_1_results`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-11ac5eb8d9e9032c'}}
# model_1 <- ...(..., ...)

# model_1_results <- ...(..., ...) %>% mutate_if(is.numeric, round, 2)
# model_1_results

### BEGIN SOLUTION

model_1 <- lm(y ~ x_1 + x_2, data = sample_model_1)

model_1_results <- tidy(model_1, conf.int = TRUE) %>% mutate_if(is.numeric, round, 2)
model_1_results

### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-326617182b53a8b9'}}
test_2.1()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-453527ccc61f4adf"} -->
#### Note that the estimates $\hat{\beta}_0$,  $\hat{\beta}_1$, and $\hat{\beta}_2$ in `model_1` are close to the true population parameters (less than 2 standard errors away). At least for this sample, all 95% confidence intervals contain the true parameters that we've used to generate the data.

> **Heads up**: in general, we don't know the true parameters to make this type of assessment.
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-9939f20b71f46f90"} -->
### Heteroscedasticity

In the previous case, we assume that the error terms were independent and identically distributed. *What would happen if this assumption is not true in the data??*. In particular, we will focus on a problem known as *heteroscedasticity* which occurs when the variance of the error terms are not always the same for all observations. For example, in general, there is more variation in the income value of people with higher levels of education.

In the next question, we are going to use a data generating process with heteroscedasticity and use `lm` to estimate the coefficients of the MLR ignoring that the error terms are heteroscedastic.
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-774140056a754948"} -->
**Question 2.2**
<br>{points: 1}

We generate a sample of size $n = 1000$ from a data generating process with the following characteristics:

For $i = 1, \dots, n$:

$$Y_i = \beta_0 + \beta_1 X_{i1} + \beta_2 X_{i2} + \varepsilon_i$$ 

where the error terms $\varepsilon_i \sim \mathcal{N}(0, \sigma_i^2 = (X_{i1})^4)$. The variables $Y_i$, $X_{i1}$ and $X_{i2}$ are the same as those in question 3.0.

> **There is heteroscedasticity (i.e., the value of $\sigma_i^2$ is different for each observation).**

As before, let the true (population) regression terms $\beta_0$, $\beta_1$, and $\beta_2$ be $10$, $8$, and $5$. 

Call this new sample `sample_model_2`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-7be37d4514cec87d'}}
set.seed(321) # DO NOT CHANGE!

# sample_model_2 <- tibble(
#   x_1 = runif(n = ..., ..., ...),
#   x_2 = factor(rbinom(n = ..., size = ..., prob = ...), labels=c("A", "B"))
# )
# sample_model_2$y <- ... + ... * sample_model_2$... + 5 * ifelse(sample_model_2$... == "B", 1, 0) +
#   rnorm(n = ..., mean = ..., sd = sqrt(sample_model_2$...))
# head(sample_model_2)

### BEGIN SOLUTION
set.seed(321)

sample_model_2 <- tibble(
  x_1 = runif(n = sample_size, 2, 5),
  x_2 = factor(rbinom(n = sample_size, size = 1, prob = 0.5), labels=c("A", "B"))
)
sample_model_2$y <- 10 + 8 * sample_model_2$x_1 + 5 * ifelse(sample_model_2$x_2 == "B", 1, 0) +
  rnorm(n = sample_size, mean = 0, sd = (sample_model_2$x_1)^2)
head(sample_model_2)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-fa963f6510742705'}}
test_2.2()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-2554fcc8ead9b506"} -->
**Question 2.3**
<br>{points: 1}

Use the simulated `sample_model_2` to estimate the regression parameters $\beta_0$, $\beta_1$, and $\beta_2$ and elements to make inference using hypothesis tests. 

*Ignore the heteroscedasticity of the data generating process* and use the function `lm()` to estimate the regression parameters. Assign the results to the object `model_2`.

Obtain the estimated coefficients, their standard errors, corresponding $p$-values, $95\%$ confidence intervals using `tidy()`. Store the results in `model_2_results`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-a4752931d34821b5'}}
# model_2 <- ...(..., ...)

# model_2_results <- ...(..., ...) %>% mutate_if(is.numeric, round, 2)
# model_2_results

### BEGIN SOLUTION

model_2 <- lm(y ~ x_1 + x_2, data = sample_model_2)

model_2_results <- tidy(model_2, conf.int = TRUE) %>% mutate_if(is.numeric, round, 2)
model_2_results

### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-cb5ea4ece832800f'}}
test_2.3()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-358b448fd8b907f1"} -->
**Question 2.4**
<br>{points: 1}

Recall that the true population values of $\beta_0$, $\beta_1$, and $\beta_2$ are $10$, $8$, and $5$ respectively.  What of the following consequences of ignoring the heteroscedasticity of the data generating process is true? 

*Tip*: `lm` assumes that the errors are *iid* as in `sample_model_1`. Thus, you can also use `model_1_results` as a benchmark.

**A.** The estimates $\hat{\beta}_0$,  $\hat{\beta}_1$, and $\hat{\beta}_2$ in `model_2_results` are still similar to the true population parameters but their estimated standard errors are inflated.

**B.** The 95% confidence intervals of the regression coefficients are not affected by the heteroscedasticity of the data generating process.


*Assign your answer to an object called `answer3.4`. Your answer should be one of `"A"` or `"B"` surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-03200e468b4ed9a7'}}
# answer2.4 <- 

### BEGIN SOLUTION
answer2.4 <- "A"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-d4fa23719518cfae'}}
test_2.4()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-e51a3e421545b891"} -->
#### Detecting heteroscedasticity

When we don't have simulated data, we can (graphically) diagnose heteroscedasticity by comparing the fitted values to the residuals. If the errors are homoscedastic (equal variance), the residuals should show equal variation for all fitted values. 

Let's take a look at these plots for both cases simulated before: `model_1` (homoscedastic case) versus `model_2` (heteroscedastic case). We can obtain both plots via the function `plot()`.

*Uncomment and run the cell below before continuing.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': False, 'locked': True, 'task': False, 'grade_id': 'cell-f9d678639aeb4975'}}
# plot(model_1, 1, main = "Model 1: homoscedastic")
# plot(model_2, 1, main = "Model 2: heteroscedastic")

### BEGIN SOLUTION
plot(model_1, 1, main = "Model 1: homoscedastic")
plot(model_2, 1, main = "Model 2: heteroscedastic")
### END SOLUTION
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-2423a377827ef0db"} -->
**Question 2.5**
<br>{points: 1}

What is the difference between both plots of residuals versus fitted values?

**A.** There is no difference between both plots; their respective clouds of points look uniformly similar.

**B.** The diagnostic plot of `model_1` shows a uniform and more scattered cloud of points than `model_2`. The cloud of points in `model_2` shows a clear funnel shape, indicating a non-constant variance.

**C.** The diagnostic plot of `model_2` shows a uniform and more scattered cloud of points than `model_1`. The cloud of points in `model_1` shows a clear funnel shape, indicating a non-constant variance.

*Assign your answer to an object called `answer3.5`. Your answer should be one of `"A"`, `"B"`, or `"C"` surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-0ac7451d1055fdcd'}}
# answer2.5 <- 

### BEGIN SOLUTION
answer2.5 <- "B"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-a0823aa644741ac9'}}
test_2.5()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-32a44b64fde55ec7"} -->
### Normality

Another assumption commonly made in linear regression is that the error terms are Normally distributed. *What would happen if this assumption is not true in the data??*. 

In the next question, we are going to use a data generating process with non-normal errors and use `lm` to estimate the coefficients of the MLR.
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-0583e55524bbbff4"} -->
**Question 2.6**
<br>{points: 1}

For $i = 1, \dots, n$:

$$Y_i = \beta_0 + \beta_1 X_{i,1} + \beta_2 X_{i, 2} + \varepsilon_i$$

where the error terms are independent and identically distributed with $\varepsilon_i \sim \mathrm{t}(1)$. The variables $Y_i$, $X_{i1}$ and $X_{i2}$ are the same as those in question 3.0.

> **The errors follow a Student's *t* distribution with df =1, also known as Cauchy distribution. This is a symmetric distibution with heavy tails.**

As before, let the true (population) regression terms $\beta_0$, $\beta_1$, and $\beta_2$ be $10$, $8$, and $5$. 

Call this new sample `sample_model_3`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-f4f0d75b03d87416'}}
set.seed(654) # DO NOT CHANGE!

# sample_model_3 <- tibble(
#   x_1 = runif(n = ..., ..., ...),
#   x_2 = factor(rbinom(n = ..., size = ..., prob = ...), labels=c("A", "B"))
# )
# sample_model_3$y <- ... + .. * sample_model_3$... + 5 * ifelse(sample_model_3$... == "B", 1, 0) +
#   ...(n = ..., min = ..., max = ...)
# head(sample_model_3)

### BEGIN SOLUTION
set.seed(654)

sample_model_3 <- tibble(
  x_1 = runif(n = sample_size, 2, 5),
  x_2 = factor(rbinom(n = sample_size, size = 1, prob = 0.5), labels=c("A", "B"))
)
sample_model_3$y <- 10 + 8 * sample_model_3$x_1 + 5 * ifelse(sample_model_3$x_2 == "B", 1, 0) +
  rt(n = sample_size, df = 1)
head(sample_model_3)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-4daac39e2a263638'}}
test_2.6()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-31286491f37e5adf"} -->
**Question 2.7**
<br>{points: 1}

Use the simulated `sample_model_3` to estimate the regression parameters $\beta_0$, $\beta_1$, and $\beta_2$ and elements to make inference using hypothesis tests. 

Use the function `lm()` to estimate the regression parameters. Assign the results to the object `model_3`.

Obtain the estimated coefficients, their standard errors, corresponding $p$-values, $95\%$ confidence intervals using `tidy()`. Store the results in `model_3_results`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-265c75bbb081eb6f'}}
# model_3 <- ...(..., ...)

# model_3_results <- ...(..., ...) %>% mutate_if(is.numeric, round, 2)
# model_3_results

### BEGIN SOLUTION

model_3 <- lm(y ~ x_1 + x_2, data = sample_model_3)

model_3_results <- tidy(model_3, conf.int = TRUE) %>% mutate_if(is.numeric, round, 2)
model_3_results

### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-9cc9196c59e66f46'}}
test_2.7()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-e68f5ba3f0ccd35f"} -->
#### Note that the estimate of the regression parameters are not heavily affected by this problem. 

The distributions of the test statistics such as the $t$ or the $F$-statistics rely on the normality of the $\varepsilon_i$s, unless the sample size $n$ is large enough in which case their distribution can be approximated using asymptotic results. 

#### Note that in this case, the sample size is large so the CLT can be used to approximate the sampling distributions. Thus, the confidence intervals are also similar to those of `model_1_results`. 
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-8ae11e452b9ab56f"} -->
#### Diagnostic plots

A $Q$-$Q$ plot and the histogram of residuals are graphical tools that help us to assess the normality assumption as follows:

- In the case of the $Q$-$Q$ plot, the ideal result is having all the data points lying on the 45° degree dotted line. This result means that all standardized residuals coming from the fitted model are equal to the theoretical quantiles coming from the standard normal distribution, i.e., $\mathcal{N}(0, 1)$. 

- For the histogram of residuals, we would expect a bell-shaped form as in the normal distribution. 

Let us compare these plots for `model_1` (with Normal errors) and `model_3` (with non-Normal errors). We can obtain both $Q$-$Q$ plots via the function `plot()` and the histograms using `hist()`.

*Uncomment and run the cell below before continuing.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': False, 'locked': True, 'task': False, 'grade_id': 'cell-376408f168bc4a00'}}
# plot(model_1, 2, main = "Model 1")
# hist(residuals(object = model_1),
#   breaks = 10,
#   main = "Histogram of Residuals for Model 1",
#   xlab = "Residuals"
# )

# plot(model_3, 2, main = "Model 3")
# hist(residuals(object = model_3),
#   breaks = 10,
#   main = "Histogram of Residuals for Model 3",
#   xlab = "Residuals"
# )

### BEGIN SOLUTION
plot(model_1, 2, main = "Model 1")
hist(residuals(object = model_1),
  breaks = 10,
  main = "Histogram of Residuals for Model 1",
  xlab = "Residuals"
)

plot(model_3, 2, main = "Model 3")
hist(residuals(object = model_3),
  breaks = 10,
  main = "Histogram of Residuals for Model 3",
  xlab = "Residuals"
)
### END SOLUTION
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-3ef9ae8e1ccaf538"} -->
**Question 2.8**
<br>{points: 1}


What is the difference between both pairs plots corresponding to `model_1` and `model_3`?

**A.** There are no differences between both pairs of plots, suggesting that both models fulfil the normality assumption.

**B.** For `model_3`, most of the points lie on the 45° degree dotted line of the $Q$-$Q$ plot suggesting that the errors are normally distributed. 

**C.** For `model_1`, most of the points lie on the 45° degree dotted line of the $Q$-$Q$ plot suggesting that the errors are normally distributed. 

**D.** The histogram of the residuals of `model_3` is similar to that of the residuals of `model_1`. 

*Assign your answer to an object called `answer3.8`. Your answer should be one of `"A"`, `"B"`, `"C"`, or `"D"`, surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-322d6b07e2c76409'}}
# answer2.8 <- 

### BEGIN SOLUTION
answer2.8 <- "C"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-7cfdd3595723b330'}}
test_2.8()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-f3685cd190b2a48e"} -->
### Multicollinearity

A common problem in real data occurs when the input variables are correlated. This problem is known as multicollinearity. In this section we will simulate correlated input variables to understand how this problem affects the sampling distribution of the least squares regression parameter estimators.
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-08094e7e680afc80"} -->
In this exercise, we will generate 1000 sample of size $n = 100$ from the following data generating process:

For $i = 1, \dots, n$,

$$Y_i = \beta_0 + \beta_1 X_{i1} + \beta_2 X_{i2} + \varepsilon_i$$ 

where the error terms $\varepsilon_i \sim \mathcal{N}(0, \sigma^2 = 4)$ are independent and identically distributed, and $X_{1}$ and $X_{2}$ are two continuous correlated input variables. 

Assume that all the true (population) regression terms $\beta_0$, $\beta_1$, and $\beta_2$ are equal to $10$. 
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-c521effc05929e77"} -->
**Question 2.9**
<br>{points: 1}

First, let's learn how to generate correlated inputs $X_{1}$ and $X_{2}$ from a bivariate normal distribution. Assume these variables have population means $\mu_1 = 10$ and $\mu_2 = 20$, respectively. Furthermore, their respective population variances are $\sigma_1 = 4$ and  $\sigma_2 = 8$ and a correlation $\rho = 0.95$ to generate multicollinearity.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-1f1c93e7aa03af7d'}}
set.seed(456) # DO NOT CHANGE!

# bivariate_normal_sample <- rnorm_multi(
#   n = ...,
#   mu = c(...,...)
#   sd = c(...,...)
#   r = ...,
#   varnames = c("x_1", "x_2"),
#   empirical = FALSE
# )

# head(bivariate_normal_sample)

### BEGIN SOLUTION
set.seed(456)

bivariate_normal_sample <- rnorm_multi(
  n = 1000,
  mu = c(10, 20),
  sd = c(4, 8),
  r = 0.95,
  varnames = c("x_1", "x_2"),
  empirical = FALSE
)

head(bivariate_normal_sample)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-da29435913bf774f'}}
test_2.9()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-db19c531325127ad"} -->
**Question 2.10**
<br>{points: 1}

Now we generate $1000$ datasets of size $n=100$ from the data generating process described and fit an additive MLR using `lm` to each dataset. 

Store the corresponding $\hat{\beta}_0$, $\hat{\beta}_1$, and $\hat{\beta}_2$ per sample in a dataframe called `lm_multicollinearity` of 1000 rows and three columns:

- intercept: The estimated intercept $\hat{\beta}_0$.
- beta_1_hat: The estimated slope $\hat{\beta}_1$.
- beta_2_hat: The estimated slope $\hat{\beta}_2$.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-7fc8624a0cab3f0e'}}
set.seed(321) # DO NOT CHANGE!

# sample_size <- ...
# num_replicates <- ...

# beta_0 <- ...
# beta_1 <- ...
# beta_2 <- ...

# lm_multicollinearity <- replicate(..., {
#   rnorm_multi(
#     n = ...,
#     mu = ...,
#     sd = ...,
#     r = ...,
#     varnames = c("x_1", "x_2"),
#     empirical = FALSE
#   ) %>%
#     mutate(y = ... + beta_1 * ... + ... * x_2 +
#       rnorm(n = ..., mean = 0, sd = ...)) %>%
#     lm(..., data = .) %>%
#     .$coef
# })
# lm_multicollinearity <- data.frame(
#   intercept = lm_multicollinearity[1, ],,
#   beta_1_hat = lm_multicollinearity[2, ],,
#   beta_2_hat = lm_multicollinearity[3, ],
# )

# head(lm_multicollinearity_dist)

### BEGIN SOLUTION
set.seed(321)

sample_size <- 100
num_replicates <- 1000

beta_0 <- 10
beta_1 <- 10
beta_2 <- 10

lm_multicollinearity <- replicate(num_replicates, {
  rnorm_multi(
    n = sample_size,
    mu = c(10, 20),
    sd = c(4, 8),
    r = c(0.95),
    varnames = c("x_1", "x_2"),
    empirical = FALSE
  ) %>%
    mutate(y = beta_0 + beta_1 * x_1 + beta_2 * x_2 +
      rnorm(n = sample_size, mean = 0, sd = 2)) %>%
    lm(formula = y ~ x_1 + x_2, data = .) %>%
    .$coef
})
lm_multicollinearity <- data.frame(
  intercept = lm_multicollinearity[1, ],
  beta_1_hat = lm_multicollinearity[2, ],
  beta_2_hat = lm_multicollinearity[3, ]
)

head(lm_multicollinearity)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'grade_id': 'cell-a3ad21c32c86b702', 'points': 1}}
test_2.10()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-a420aafa6b0d76a6"} -->
**Question 2.11**
<br>{points: 1}

For comparison purposes, repeat the process for samples taken from a population without multicollinearity (use $\rho = 0.001$).

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-a62dc494d2cb00f0'}}
set.seed(321) # DO NOT CHANGE!

# sample_size <- ...
# num_replicates <- ...

# beta_0 <- ...
# beta_1 <- ...
# beta_2 <- ...

# lm_no_multicollinearity <- replicate(..., {
#   rnorm_multi(
#     n = ...,
#     mu = ...,
#     sd = ...,
#     r = ...,
#     varnames = c("x_1", "x_2"),
#     empirical = FALSE
#   ) %>%
#     mutate(y = ... + beta_1 * ... + ... * x_2 +
#       rnorm(n = ..., mean = 0, sd = ...)) %>%
#     lm(..., data = .) %>%
#     .$coef
# })
# lm_no_multicollinearity <- data.frame(
#   intercept = lm_no_multicollinearity[1, ],,
#   beta_1_hat = lm_no_multicollinearity[2, ],,
#   beta_2_hat = lm_no_multicollinearity[3, ],
# )

# head(lm_no_multicollinearity_dist)

### BEGIN SOLUTION
set.seed(321)

sample_size <- 100
num_replicates <- 1000

beta_0 <- 10
beta_1 <- 10
beta_2 <- 10

lm_no_multicollinearity <- replicate(num_replicates, {
  rnorm_multi(
    n = sample_size,
    mu = c(10, 20),
    sd = c(4, 8),
    r = c(0.001),
    varnames = c("x_1", "x_2"),
    empirical = FALSE
  ) %>%
    mutate(y = beta_0 + beta_1 * x_1 + beta_2 * x_2 +
      rnorm(n = sample_size, mean = 0, sd = 2)) %>%
    lm(formula = y ~ x_1 + x_2, data = .) %>%
    .$coef
})
lm_no_multicollinearity <- data.frame(
  intercept = lm_no_multicollinearity[1, ],
  beta_1_hat = lm_no_multicollinearity[2, ],
  beta_2_hat = lm_no_multicollinearity[3, ]
)

head(lm_no_multicollinearity)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-79f290838673f039'}}
test_2.11()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-afc49b8f8185ea46"} -->
**Question 2.12**
<br>{points: 1}

Plot the 1000 regression estimates for the slope corresponding to $X_1$ (i.e., $\hat{\beta}_1$) stored in `lm_multicollinearity` and `lm_no_multicollinearity`, separately (i.e., two histograms with counts on the $y$-axis and the estimate on the $x$-axis). 

Call the ggplot() object's names `hist_multicollinearity_slope_x_1` and `hist_no_multicollinearity_slope_x_1`, respectively. Moreover, plot the averages of these estimates in their respective histograms as vertical red lines.

*Fill out those parts indicated with ..., uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-567626205f418eb8'}}
options(repr.plot.width = 15, repr.plot.height = 7) # Adjust these numbers so the plot looks good in your desktop.

# hist_multicollinearity_slope_x_1 <- ggplot(..., aes(...)) +
#   ...(bins = 15, color = "black", fill = "blue") +
#   ...(..., col = "red", size = 1) +
#   coord_cartesian(xlim = c(9.4, 10.6), ylim = c(0, 250)) +
#   scale_x_continuous(breaks = seq(9, 10.6, 0.2)) +
#   xlab(...) +
#   ylab(...) +
#   theme(
#     text = element_text(size = 19),
#     plot.title = element_text(face = "bold"),
#     axis.title = element_text(face = "bold")
#   ) +
#   ggtitle(...)

# hist_no_multicollinearity_slope_x_1 <- ggplot(..., aes(...)) +
#   ...(bins = 15, color = "black", fill = "blue") +
#   ...(..., col = "red", size = 1) +
#   coord_cartesian(xlim = c(9.4, 10.6), ylim = c(0, 250)) +
#   scale_x_continuous(breaks = seq(9, 10.6, 0.2)) +
#   xlab(...) +
#   ylab(...) +
#   theme(
#     text = element_text(size = 19),
#     plot.title = element_text(face = "bold"),
#     axis.title = element_text(face = "bold")
#   ) +
#   ggtitle(...)

# plot_grid(hist_multicollinearity_slope_x_1, hist_no_multicollinearity_slope_x_1,
#   ncol = 2
# )

### BEGIN SOLUTION
hist_multicollinearity_slope_x_1 <- ggplot(lm_multicollinearity, aes(x = beta_1_hat)) +
  geom_histogram(bins = 15, color = "black", fill = "blue") +
  geom_vline(aes(xintercept = mean(beta_1_hat)), col = "red", size = 1) +
  coord_cartesian(xlim = c(9.4, 10.6), ylim = c(0, 250)) +
  scale_x_continuous(breaks = seq(9, 10.6, 0.2)) +
  xlab("Estimated Slope") +
  ylab("Count") +
  theme(
    text = element_text(size = 19),
    plot.title = element_text(face = "bold"),
    axis.title = element_text(face = "bold")
  ) +
  ggtitle(expression("Distribution of" ~ hat(beta)[1] ~ "with Multicollinearity"))

hist_no_multicollinearity_slope_x_1 <- ggplot(lm_no_multicollinearity, aes(x = beta_1_hat)) +
  geom_histogram(bins = 15, color = "black", fill = "blue") +
  geom_vline(aes(xintercept = mean(beta_1_hat)), col = "red", size = 1) +
  coord_cartesian(xlim = c(9.4, 10.6), ylim = c(0, 250)) +
  scale_x_continuous(breaks = seq(9, 10.6, 0.2)) +
  xlab("Estimated Slope") +
  ylab("Count") +
  theme(
    text = element_text(size = 19),
    plot.title = element_text(face = "bold"),
    axis.title = element_text(face = "bold")
  ) +
  ggtitle(expression("Distribution of" ~ hat(beta)[1] ~ "without Multicollinearity"))

plot_grid(hist_multicollinearity_slope_x_1, hist_no_multicollinearity_slope_x_1,
  ncol = 2
)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-7660d122189e5eb7'}}
test_2.12.0()
test_2.12.1()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-a3e0187538a817b4"} -->
**Question 2.13**
<br>{points: 1}

Based on your findings in `hist_multicollinearity_slope_x_1` and `hist_no_multicollinearity_slope_x_1`, what are the implications of multicollinearity in the sampling distributions of least squares estimators of MLR?

**A.** Multicollinearity does not seem to affect the expected value of the slope estimator. Nonetheless, multicollinearity decreases the variance of the estimator. This phenomenon reduces the standard error, which also reduces the power of the test to detect a significant non-zero slope $\beta_1$.

**B.** Multicollinearity does not seem to affect the expected value of the slope estimator. Nonetheless, multicollinearity increases the variance of the estimator. This phenomenon inflates the standard error, which reduces the power of the test to detect a significant non-zero slope $\beta_1$.

**C.** Multicollinearity seems to affect the expected value of the slope estimator and decreases the variance of the estimator. This phenomenon reduces the standard error, which increases the power of the test to detect a significant non-zero slope $\beta_1$.

*Assign your answer to an object called answer3.13. Your answer should be one of `"A"`, `"B"`, or `"C"` surrounded by quotes.*

<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-13a2606b42741a5e'}}
# answer2.13 <- ...

### BEGIN SOLUTION
answer2.13 <- "B"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-93b7a249a29267bc'}}
test_2.13()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-ddd9186d674cb006"} -->
# PART II
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-79db06e3c76c8b52"} -->
## 2.  Causality and Confounders

In this section we will explore the problem of confounders in causal inference using a simulation. 

Roughly speaking, in a framework where $X$ is the input variable and $Y$ is the response, another input variable $C$ confounds the $X$-$Y$ relationship if $C$ and $X$ are associated, and $C$ and $Y$ are associated. 

Let us retake the example from `worksheet_01` and `tutorial_01` of an A/B testing involving two versions of a TikTok ad:

- Suppose a sport company's marketing team has developed a new video for their TikTok ad. They want to know if this **new** ad will **INCREASE** the ad engagement (which they will measure via the *ad dwell time* in seconds, i.e., a continuous response) compared to the **current** ad they are running in a given customer population.
- Furthermore, let us make the framework more complex. Suppose that athletes in this population have larger dwell times and are more interested to innovations by the company. 
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-5ede733844d163fc"} -->
**Question 3.0**
<br>{points: 1}

Under this framework, what is the response $Y$?

**A.** Type of TikTok ad.

**B.** Ad dwell time.

**C.** Athlete (yes/no).

*Assign your answer to the object `answer2.0`. Your answer should be one of `"A"`, `"B"`, or `"C"` surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-5b816fdc7b09019e'}}
# answer3.0 <- 

### BEGIN SOLUTION
answer3.0 <- "B"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-c699cf97e489b92a'}}
test_3.0()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-fc0754257c27c1e8"} -->
**Question 3.1**
<br>{points: 1}

What is the main input of interest $X$?

**A.** Type of TikTok ad.

**B.** Ad dwell time.

**C.** Athlete (yes/no).

*Assign your answer to the object `answer2.1`. Your answer should be one of `"A"`, `"B"`, or `"C"` surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-e73540a8ff5f8b82'}}
# answer3.1 <- 

### BEGIN SOLUTION
answer3.1 <- "A"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-e94b4f797404d439'}}
test_3.1()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-2abb4b32b65f2802"} -->
**Question 3.2**
<br>{points: 1}

True or False?

If we regress the dwell time on the type of add, ignoring which customers are athletes, the results of the estimation will be counfounded.

*Assign your answer to an object called `answer2.2`. Your answer should be either "true" or "false", surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-f1d4af5d171fc51b'}}
# answer3.2 <- 

### BEGIN SOLUTION
answer3.2 <- "true"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-68e19c3e379d332f'}}
test_3.2()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-24d7242a5a8dd9c1"} -->
There is more than one way to deal with confounding factors if we want to detect a causal relationship between $X$ and $Y$. Depending on the nature of the study, one could do the following:

1. In the case of observational studies, stratification is a good strategy. It implies checking the association between $X$ and $Y$ within subgroups of observations that share common values for the confounder(s). 
2. In an experimental study, such as A/B testing, we would randomize each subject to a particular value of $X$. Then, we compare $Y$ across the different groups of $X$. 

> **Heads-up:** The second strategy is the golden standard in causal inference. Nonetheless, it is not always practical or even ***ETHICAL*** to randomly assign experimental units to experimental groups.
<!-- #endregion -->

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-3087592c11275814"} -->
**Question 3.3**
<br>{points: 1}

We will start by building a synthetic population for the TikTok ad case. Suppose this population has `1000000` customers (`pop.size`), where 50% are athletes and another 50% are not (i.e., a categorical variable called `athlete` with levels "Y" and "N"). 

Build a tibble containing all the customers in the population called `pop.pool` with a column for `athlete`. The values in this column needs to be simulated, as explained above. Input the count of `Y` values in `pop.pool` into the variable `pop.pool.Y`

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-a07659e2ca3f9b67'}}
set.seed(123) # DO NOT CHANGE!

# pop.size <- ...

# pop.pool <- tibble(
#   athlete = sample(c(rep("Y", ...), rep("N", ...))),
# )
# head(pop.pool)
# pop.pool.Y <- sum(...)

### BEGIN SOLUTION
set.seed(123)
pop.size <- 1000000

pop.pool <- tibble(
  athlete = sample(c(rep("Y", pop.size / 2), rep("N", pop.size / 2))),
)

head(pop.pool)
pop.pool.Y <- sum(pop.pool == "Y")
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-3690173f6b9608c6'}}
test_3.3()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-3eb9200dec60c3a5"} -->
**Question 3.4**
<br>{points: 1}
 
Once we have our population pool of customers, we need to simulate their corresponding dwell times $Y$ either if they see the current or the new ad. Hence, each customer in the population will have a pair of potential responses: one for the current ad and one for the new ad in seconds. We will later assign one of these to each customer.

Within the population, both responses will have their own means *per customer* as follows:
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': False, 'locked': True, 'task': False, 'grade_id': 'cell-ccd1c59a2c683ee0'}}
# Run this cell before continuing.

mean_current_ad <- 15 + 5 * (pop.pool$athlete == "Y")
round(head(mean_current_ad), 4)

mean_new_ad <- mean_current_ad + 8
round(head(mean_new_ad), 4)
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-9f6dc1586d857ea9"} -->
The code above is computing response means in seconds for each customer within `pop.pool`, according to their sport experience (athlete vs non-athlete):

- `mean_current_ad`: This is the vector of `1000000` response means corresponding to the current video. It has a baseline of `15` seconds for each customer, plus `5` additional seconds if the customer is an athlete.
- `mean_new_ad`: This is the vector of `1000000` response means corresponding to the new video. It is just the vector `mean_current_ad` plus `8` seconds for *all* the customers. 

> **Note that the value of `8` in `mean_new_ad` is the one we aim to estimate, which indicates that the new ad increases the dwell time by 8 seconds in the customer population.**

Once we have these vectors of means, we can simulate the corresponding response means `y_current_ad` and `y_new_ad` and incorporate them in `pop.pool` as two new columns. These responses will be normally distributed (i.e., we use `rnorm()` to generate the values) with means `mean_current_ad` and `mean_new_ad` and fixed standard deviations of 1 second.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-36a6f82a24a27671'}}
set.seed(123) # DO NOT CHANGE!

# pop.pool$y_current_ad <- ...(..., ..., ...)
# pop.pool$y_new_ad <- ...(..., ..., ...)
# head(pop.pool)

### BEGIN SOLUTION
set.seed(123)

pop.pool$y_current_ad <- rnorm(pop.size, mean = mean_current_ad, sd = 1)
pop.pool$y_new_ad <- rnorm(pop.size, mean = mean_new_ad, sd = 1)
head(pop.pool)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-199e9db6bdca3064'}}
test_3.4()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-c1dd7c888d0b7499"} -->
**Question 3.5**
<br>{points: 1}

Now that we have all the values from the populations of interest, we can generate a sample with the characteristics of an observational study. That is, we simulate a situation in which each customer chooses the type of ad to be seen.
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': False, 'locked': True, 'task': False, 'grade_id': 'cell-09781fa051fa4a20'}}
# Run this cell before continuing.

set.seed(123)

pop.pool$x_self_choice <- factor(rbinom(pop.size,
  size = 1,
  prob = 0.5 + 0.5 * (pop.pool$athlete == "Y")), labels = c("Current", "New"))
head(pop.pool)
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-6699bad04977ecb9"} -->
The code above creates a factor-type column called `x_self_choice` from a binomial distribution whose probability of success (i.e., choosing the new ad) increases when the customer is an athlete (check argument `prob` in `rbinon()`). Note that the factor levels in `x_self_choice` are labeled as `Current` for `0` and `New` for `1`.

Create another column in `pop.pool` called `y_obs`, which will contain the observed response by customer based on `x_self_choice`; i.e., **IF** the customer is more likely to choose the `New` ad then the column `y_obs` will contain the value indicated in `y_new_ad`, **ELSE** otherwise. Then, from `pop.pool`, collect one sample of size `1000` and call it `sample_TikTok`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-a7e28e22d1467fa0'}}
set.seed(123) # DO NOT CHANGE!

# pop.pool$y_obs <- ...(...,
#   ..., ...
# )

# sample_obs_study <- ...(pop.pool, ...)
# head(sample_obs_study)

### BEGIN SOLUTION
set.seed(123)

pop.pool$y_obs <- ifelse(pop.pool$x_self_choice == "Current",
  pop.pool$y_current_ad, pop.pool$y_new_ad
)

sample_TikTok <- rep_sample_n(pop.pool, size = 1000)
head(sample_TikTok)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-221d0a1c04de31c5'}}
test_3.5()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-4661d9eda28c67b6"} -->
**Question 3.6**
<br>{points: 1}

We need to graphically compare the observed distributions and spread in both ads within `sample_TikTok` via side-by-side boxplots. The `ggplot()` object's name will be `obs_dwell_time_boxplots`. Note that function `stat_summary()` will need to add the treatment means as points on top of each boxplot.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-1b8395e5100f01ae'}}
options(repr.plot.width = 15, repr.plot.height = 7) # Adjust these numbers so the plot looks good in your desktop.

# obs_dwell_time_boxplots <- ... %>%
#   ggplot() +
#   ...(aes(..., ..., fill = ...)) +
#   theme(
#     text = element_text(size = 22),
#     plot.title = element_text(face = "bold"),
#     axis.title = element_text(face = "bold")
#   ) +
#   ggtitle(...) +
#   xlab(...) +
#   ylab(...) +
#   stat_summary(aes(..., ..., fill = ...),
#     fun = ..., colour = "yellow", geom = "point",
#     shape = 18, size = 5
#   )
# obs_dwell_time_boxplots

### BEGIN SOLUTION
obs_dwell_time_boxplots <- sample_TikTok %>%
  ggplot() +
  geom_boxplot(aes(x_self_choice, y_obs, fill = x_self_choice)) +
  theme(
    text = element_text(size = 22),
    plot.title = element_text(face = "bold"),
    axis.title = element_text(face = "bold")
  ) +
  ggtitle("Observed Dwell Times") +
  xlab("Type") +
  ylab("Dwell Time (seconds)") +
  stat_summary(aes(x_self_choice, y_obs, fill = x_self_choice),
    fun = mean, colour = "yellow", geom = "point",
    shape = 18, size = 5
  )
obs_dwell_time_boxplots
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-074e5d1b1900eb51'}}
test_3.6()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-0849144833b53dc9"} -->
**Question 3.7**
<br>{points: 1}

Now let's analyze the data collected in an observational study from `sample_TikTok`. Imagine that we only collect the dwell times and the type of chosen ad. Suppose you want to estimate the **real population effect** in the dwell time of the new ad compared to the current ad. Recall we set up our synthetic data in such a way this effect is an increase of 8 seconds.

Using `sample_TikTok`, estimate a linear regression called `conf_obs_study_TikTok` of the dwell time (`y_obs`) versus the chosen type of ad (`x_self_choice`). Report the estimated coefficients, their standard errors, and corresponding $p$-values using `tidy()`. Include the corresponding asymptotic 95% confidence intervals. Store the results in the variable `conf_obs_study_TikTok_results`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-1f03dc55e81a815b'}}
# conf_obs_study_TikTok <- ...(...,
#   ...
# )
# conf_obs_study_TikTok

# conf_obs_study_TikTok_results <- ...(..., ...) %>% mutate_if(is.numeric, round, 2)
# conf_obs_study_TikTok_results

### BEGIN SOLUTION
conf_obs_study_TikTok <- lm(y_obs ~ x_self_choice,
  data = sample_TikTok
)
conf_obs_study_TikTok

conf_obs_study_TikTok_results <- tidy(conf_obs_study_TikTok, conf.int = TRUE) %>% mutate_if(is.numeric, round, 2)
conf_obs_study_TikTok_results
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-2aee3b28600b82d8'}}
test_3.7()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-124ee4343db07e2e"} -->
**Question 3.8**
<br>{points: 1}

Based on your output in `conf_obs_study_TikTok_results`, what can we conclude on the estimation of the population effect of the new ad?

**A.** The estimated effect in dwell time when switching from the current to the new ad increases by 11.46 seconds. The effect is largely overestimated in this analysis.

**B.** The estimated effect in dwell time when switching from the current to the new ad increases by 11.46 seconds. The effect is largely underestimated in this analysis.

**C.** The estimated effect in dwell time when switching from the new to the current ad increases by 11.46 seconds. The effect is largely overestimated in this analysis.

**D.** The estimated effect in dwell time when switching from the new to the current ad increases by 11.46 seconds. The effect is largely underestimated in this analysis.

*Assign your answer to an object called `answer2.8`. Your answer should be one of `"A"`, `"B"`, `"C"`, or `"D"` surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-86428c144337095e'}}
# answer3.8 <- 

### BEGIN SOLUTION
answer3.8 <- "A"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-b39949791a043f72'}}
test_3.8()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-f381389024b4b3d1"} -->
**Question 3.9**
<br>{points: 1}

Now, let us suppose we can collect additional information about the customers. In particular, we add information about the sport experience of the custormers contained in the variable `athlete` in `sample_TikTok`.

Estimate a MLR called `MLR_obs_study_TikTok` of the dwell time (`y_obs`) versus the type of ad and the respective confounders. Report the estimated coefficients, their standard errors, and corresponding $p$-values using `tidy()`. Include the corresponding asymptotic 95% confidence intervals. Store the results in the variable `MLR_obs_study_TikTok_results`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-d2f8094895ffcbe0'}}
# MLR_obs_study_TikTok <- ...(...,
#   ...
# )
# MLR_obs_study_TikTok

# MLR_obs_study_TikTok_results <- ...(..., ...) %>% mutate_if(is.numeric, round, 2)
# MLR_obs_study_TikTok_results

### BEGIN SOLUTION
MLR_obs_study_TikTok <- lm(y_obs ~ x_self_choice + athlete,
  data = sample_TikTok
)
MLR_obs_study_TikTok

MLR_obs_study_TikTok_results <- tidy(MLR_obs_study_TikTok, conf.int = TRUE) %>% mutate_if(is.numeric, round, 2)
MLR_obs_study_TikTok_results
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-aa1351a49c6670ac'}}
test_3.9()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-eea40beb179b70d6"} -->
**Question 3.10**
<br>{points: 1}

Based on your output in `MLR_obs_study_TikTok_results`, how does the estimation of the effect of the new ad change when the confounder is included in the model?

**A.** The estimated effect in dwell time when switching from the current to the new ad increases by 8.08 seconds. The effect is largely underestimated in this analysis.

**B.** The estimated effect in dwell time when switching from the new to the current ad increases by 8.08 seconds. Controlling for the causal confounders provides an accurate effect estimate.

**C.** The estimated effect in dwell time when switching from the current to the new ad increases by 8.08 seconds. Controlling for the causal confounders provides an accurate effect estimate. 

**D.** The estimated effect in dwell time when switching from the new to the current ad increases by 8.08 seconds. The effect is largely overestimated in this analysis.

*Assign your answer to an object called `answer2.10`. Your answer should be one of `"A"`, `"B"`, `"C"`, or `"D"` surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-8eb4421ee345f4bf'}}
# answer3.10 <- 

### BEGIN SOLUTION
answer3.10 <- "C"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-25ed9c2588f8619c'}}
test_3.10()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-c7f3f34199af1535"} -->
**Question 3.11**
<br>{points: 1}

Finally, let us imagine we are able to run an experimental study (i.e., A/B testing) with the customers in `sample_TikTok` **under a balanced design**. Therefore, create a two-level factor-type column called `x_randomized` by randomly assigning each customer to view either the `Current` ad or the `New` ad. Then, create another column in `sample_TikTok` called `y_exp`, which will contain the obtained experimental response by customer based on `x_randomized`; i.e., if the customer is assigned to `New` then the column `y_exp` will contain the value indicated in `y_new_ad`, else otherwise.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-008c0bda1eff03f0'}}
set.seed(1234) # DO NOT CHANGE!

# sample_TikTok$x_randomized <- ...(c(
#   rep("Current", ...),
#   rep("New", ...)
# ))
# sample_TikTok$y_exp <- ...(...,
#   ...
# )
# head(sample_TikTok)

### BEGIN SOLUTION
set.seed(1234)

sample_TikTok$x_randomized <- sample(c(
  rep("Current", nrow(sample_TikTok) / 2),
  rep("New", nrow(sample_TikTok) / 2)
))
sample_TikTok$y_exp <- ifelse(sample_TikTok$x_randomized == "Current",
  sample_TikTok$y_current_ad, sample_TikTok$y_new_ad
)
head(sample_TikTok)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-fe37f7abf7c92bb3'}}
test_3.11()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-2af368f8d2be7c53"} -->
**Question 3.12**
<br>{points: 1}

We need to graphically compare the experimental distributions and spread in both ads within `sample_TikTok` via side-by-side boxplots. The `ggplot()` object's name will be `exp_dwell_time_boxplots`. Note that function `stat_summary()` will need to add the treatment means as points on top of each boxplot.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-00147e43530518fd'}}
# exp_dwell_time_boxplots <- ... %>%
#   ggplot() +
#   ...(aes(..., ..., fill = ...)) +
#   theme(
#     text = element_text(size = 22),
#     plot.title = element_text(face = "bold"),
#     axis.title = element_text(face = "bold")
#   ) +
#   ggtitle(...) +
#   xlab(...) +
#   ylab(...) +
#   stat_summary(aes(..., ..., fill = ...),
#     fun = ..., colour = "yellow", geom = "point",
#     shape = 18, size = 5
#   )
# plot_grid(obs_dwell_time_boxplots, exp_dwell_time_boxplots)

### BEGIN SOLUTION
exp_dwell_time_boxplots <- sample_TikTok %>%
  ggplot() +
  geom_boxplot(aes(x_randomized, y_exp, fill = x_randomized)) +
  theme(
    text = element_text(size = 22),
    plot.title = element_text(face = "bold"),
    axis.title = element_text(face = "bold")
  ) +
  ggtitle("Experimental Dwell Times") +
  xlab("Type") +
  ylab("Dwell Time (seconds)") +
  stat_summary(aes(x_randomized, y_exp, fill = x_randomized),
    fun = mean, colour = "yellow", geom = "point",
    shape = 18, size = 5
  )

plot_grid(obs_dwell_time_boxplots, exp_dwell_time_boxplots)
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-6001e1ecd13c4e3b'}}
test_3.12()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-3c56782e6f9b5253"} -->
**Question 3.13**
<br>{points: 1}

Estimate linear regression called `exp_study_TikTok` of the experimental dwell time (`y_exp`) versus the assigned type of ad (`x_randomized`). Report the estimated coefficients, their standard errors, and corresponding $p$-values using `tidy()`. Include the corresponding asymptotic 95% confidence intervals. Store the results in the variable `exp_study_TikTok_results`.

*Fill out those parts indicated with `...`, uncomment the corresponding code in the cell below, and run it.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-f8ce71be9a6d4d34'}}
# exp_study_TikTok <- ...(...,
#   ...
# )
# exp_study_TikTok

# exp_study_TikTok_results <- ...(..., ...) %>% mutate_if(is.numeric, round, 2)
# exp_study_TikTok_results

### BEGIN SOLUTION
exp_study_TikTok <- lm(y_exp ~ x_randomized,
  data = sample_TikTok
)
exp_study_TikTok

exp_study_TikTok_results <- tidy(exp_study_TikTok, conf.int = TRUE) %>% mutate_if(is.numeric, round, 2)
exp_study_TikTok_results
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-2e4f38d749647c68'}}
test_3.13()
```

<!-- #region nbgrader={"schema_version": 3, "solution": false, "grade": false, "locked": true, "task": false, "grade_id": "cell-4529ee989c1d632f"} -->
**Question 3.14**
<br>{points: 1}

Based on your output in `exp_study_TikTok_results`, coming from the experimental study, what can we conclude on the estimation of the population effect of the new ad?


**A.** The estimated effect in dwell time when switching from the new to the current ad increases by 8.02 seconds. A randomized experiment provides an accurate effect estimate without including additional variables in the model.

**B.** The estimated effect in dwell time when switching from the current to the new ad increases by 8.02 seconds. A randomized experiment provides an accurate effect estimate without including additional variables in the model.

**C.** The estimated effect in dwell time when switching from the new to the current ad increases by 8.02 seconds. The effect is largely overestimated in this analysis.

**D.** The estimated effect in dwell time when switching from the current to the new ad increases by 8.02 seconds. The effect is largely underestimated in this analysis.

*Assign your answer to an object called `answer2.14`. Your answer should be one of `"A"`, `"B"`, `"C"`, or `"D"` surrounded by quotes.*
<!-- #endregion -->

```{r nbgrader={'schema_version': 3, 'solution': True, 'grade': False, 'locked': False, 'task': False, 'grade_id': 'cell-96a817282d59e118'}}
# answer3.14 <- 

### BEGIN SOLUTION
answer3.14 <- "B"
### END SOLUTION
```

```{r nbgrader={'schema_version': 3, 'solution': False, 'grade': True, 'locked': True, 'task': False, 'points': 1, 'grade_id': 'cell-49c0fb8a0928820a'}}
test_3.14()
```
